---
title: "MS Clinical Associations"
author: "Ashika Mani"
date: "9/26/2021"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_float: yes
    number_sections: true
    toc_depth: '3'
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Variables

* T2LV_Conv - Conventional MRI T2 values
* T2LV_Subtle - Fast MRI without AI T2 values
* T2LV_SubtleMR - Fast MRI with AI T2 values
* Conv, Subtle, and SubtleMR for the variables below: 
* T1Hypo_	- T1 Hypodensity Volume 
* TBV_ Total Brain Volume
* CSF_ Total CSF Volume
* ICV_ Intracranial Volume
* LthV_ Left Thamalus Volume 
* RthV_ Right Thalamus Volume 
* GMV_ Total Gray Matter Volume
* WMV_ Total White Matter Volume
* NBV_ Normalized Brain Volume
* NThV_ Normalized Thalamic Volume
* NGMV_ Normalized Gray Matter Volume
* NWMV_ Noramlized White Matter Volume

For each of the above volumes we explored these predictor variables:

* amb=1 if PDDS $\geq$ 4, 0 if PDDS < 4 - PDDS (discrete)
* age - Age (at first scan) (continuous)
* sexbin - 1 if Female, 0 if Male
* nonhiswhite - Taken from Ethnicity and Race columns, 1 if non-hispanic european descent, 0 other
* dur - Disease Duration (date of MRI - date of first symptoms), years (continuous)
* types -  Taken from Clinical Type, 1 if RRMS and 0 other
* standard - Taken from Treatment, 1 if standard efficacy, 0 if other
* high - taken from treatment, 1 if high efficacy, 0 if other
* PDDS - PDDS (continuous)
* MSRS-R - MSRS-R (continuous)

```{r, include = FALSE}
library(readxl)
library(tidyverse)
library(skimr)
library(knitr)
library(tidyr)
library(lmerTest)
library(car)
library(plyr)
library(PowerTOST)
library(interactions)
MRIdata <- read_excel("Batch1-4_20200420.xlsx",sheet=1)
i <- c(8:48)      
MRIdata[ , i] <- apply(MRIdata[ , i], 2,           
                    function(x) as.numeric(as.character(x)))
MRIdata<-MRIdata[-c(97:124),-c(11)]
clin <- read_excel("Subtle_metadata_updated.xls",sheet=1)
clin$amb<-ifelse(clin$`PDDS Median`>=4, 1, 0)
clin$sexbin<-ifelse(clin$Sex=="Female", 1, 0) #1 if female, 0 male
clin$nonhiswhite<-ifelse((clin$Ethnicity=="Non-Hispanic" | clin$Ethnicity=="Non-hispanic")&(clin$Race=="Caucasian"), 1, 0) #1 if non-hispanic european descent, 0 other
clin<-plyr::rename(clin, c("Age (at first scan)" = "age", "Disease Duration (date of MRI - date of first symptoms), years"="dur"))
clin$types <- ifelse(clin[,14]==1,1,0) # 1 if RRMS and 0 other
clin$standard <- ifelse(clin$Treatment==1|clin$Treatment==2|clin$Treatment==3|clin$Treatment==4|clin$Treatment==5|clin$Treatment==6|clin$Treatment==18|clin$Treatment==7|clin$Treatment==8|clin$Treatment==9|clin$Treatment==10|clin$Treatment==19|clin$Treatment==20|clin$Treatment==14,1,0) # 1 if standard efficacy 0 if other
clin$high <- ifelse(clin$Treatment==16|clin$Treatment==17|clin$Treatment==15|clin$Treatment==13|clin$Treatment==11,1,0)# 1 if high efficacy 0 if other
clinical<-merge(x =MRIdata, y = clin, by="Patient ID")
clin_long <- gather(clinical, type, volume, T2LV_Conv:NWMV_SubtleMR, factor_key=TRUE)
```


# Linear model with PDDS (discrete) as a predictor variable 

## T2LV
```{r}
T2LV <-clin_long[clin_long$type == "T2LV_Conv" | clin_long$type == "T2LV_Subtle"| clin_long$type == "T2LV_SubtleMR", ]
T2LVmod <-lmer( volume ~ type * amb + age+ sexbin + nonhiswhite + dur + types + standard+high +(1 | `Patient ID`) , data=T2LV)
summary(T2LVmod)
linearHypothesis(T2LVmod, c("typeT2LV_Subtle:amb"))
linearHypothesis(T2LVmod, c("typeT2LV_SubtleMR:amb"))
```

## T1Hypo

```{r}
T1Hypo <-clin_long[clin_long$type == "T1Hypo_Conv" | clin_long$type == "T1Hypo_Subtle"| clin_long$type == "T1Hypo_SubtleMR", ]
T1Hypomod <-lmer( volume ~ type * amb + age+ sexbin + nonhiswhite + dur + types + standard+high +(1 | `Patient ID`) , data=T1Hypo)
summary(T1Hypomod)
linearHypothesis(T1Hypomod, c("typeT1Hypo_Subtle:amb"))
linearHypothesis(T1Hypomod, c("typeT1Hypo_SubtleMR:amb"))
```

## TBV

```{r}
TBV <-clin_long[clin_long$type == "TBV_Conv" | clin_long$type == "TBV_Subtle"| clin_long$type == "TBV_SubtleMR", ]
TBVmod <-lmer( volume ~ type * amb + age+ sexbin + nonhiswhite + dur + types + standard+high +(1 | `Patient ID`) , data=TBV)
summary(TBVmod)
linearHypothesis(TBVmod, c("typeTBV_Subtle:amb"))
linearHypothesis(TBVmod, c("typeTBV_SubtleMR:amb"))
```

## CSF

```{r}
CSF <-clin_long[clin_long$type == "CSF_Conv" | clin_long$type == "CSF_Subtle"| clin_long$type == "CSF_SubtleMR", ]
CSFmod <-lmer( volume ~ type * amb + age+ sexbin + nonhiswhite + dur + types + standard+high +(1 | `Patient ID`) , data=CSF)
summary(CSFmod)
linearHypothesis(CSFmod, c("typeCSF_Subtle:amb"))
linearHypothesis(CSFmod, c("typeCSF_SubtleMR:amb"))
```

## ICV

```{r}
ICV <-clin_long[clin_long$type == "ICV_Conv" | clin_long$type == "ICV_Subtle"| clin_long$type == "ICV_SubtleMR", ]
ICVmod <-lmer( volume ~ type * amb + age+ sexbin + nonhiswhite + dur + types + standard+high +(1 | `Patient ID`) , data=ICV)
summary(ICVmod)
linearHypothesis(ICVmod, c("typeICV_Subtle:amb"))
linearHypothesis(ICVmod, c("typeICV_SubtleMR:amb"))
```

## LThV

```{r}
LThV <-clin_long[clin_long$type == "LThV_Conv" | clin_long$type == "LThV_Subtle"| clin_long$type == "LThV_SubtleMR", ]
LThVmod <-lmer( volume ~ type * amb + age+ sexbin + nonhiswhite + dur + types + standard+high +(1 | `Patient ID`) , data=LThV)
summary(LThVmod)
linearHypothesis(LThVmod, c("typeLThV_Subtle:amb"))
linearHypothesis(LThVmod, c("typeLThV_SubtleMR:amb"))
```

## RThV

```{r}
RThV <-clin_long[clin_long$type == "RThV_Conv" | clin_long$type == "RThV_Subtle"| clin_long$type == "RThV_SubteMR", ]
RThVmod <-lmer( volume ~ type * amb + age+ sexbin + nonhiswhite + dur + types + standard+high +(1 | `Patient ID`) , data=RThV)
summary(RThVmod)
linearHypothesis(RThVmod, c("typeRThV_Subtle:amb"))
linearHypothesis(RThVmod, c("typeRThV_SubteMR:amb"))
```

## GMV

```{r}
GMV <-clin_long[clin_long$type == "GMV_Conv" | clin_long$type == "GMV_Subtle"| clin_long$type == "GMV_SubtleMR", ]
GMVmod <-lmer( volume ~ type * amb + age+ sexbin + nonhiswhite + dur + types + standard+high +(1 | `Patient ID`) , data=GMV)
summary(GMVmod)
linearHypothesis(GMVmod, c("typeGMV_Subtle:amb"))
linearHypothesis(GMVmod, c("typeGMV_SubtleMR:amb"))
```

## WMV

```{r}
WMV <-clin_long[clin_long$type == "WMV_Conv" | clin_long$type == "WMV_Subtle"| clin_long$type == "WMV_SubteMR", ]
WMVmod <-lmer( volume ~ type * amb + age+ sexbin + nonhiswhite + dur + types + standard+high +(1 | `Patient ID`) , data=WMV)
summary(WMVmod)
linearHypothesis(WMVmod, c("typeWMV_Subtle:amb"))
linearHypothesis(WMVmod, c("typeWMV_SubteMR:amb"))
interact_plot(WMVmod, pred = amb, modx = type)
```


## NBV

```{r}
NBV <-clin_long[clin_long$type == "NBV_Conv" | clin_long$type == "NBV_Subtle"| clin_long$type == "NBV_SubtleMR", ]
NBVmod <-lmer( volume ~ type * amb + age+ sexbin + nonhiswhite + dur + types + standard+high +(1 | `Patient ID`) , data=NBV)
summary(NBVmod)

linearHypothesis(NBVmod, c("typeNBV_Subtle:amb"))
linearHypothesis(NBVmod, c("typeNBV_SubtleMR:amb"))
```


## NThV

```{r}
NThV <-clin_long[clin_long$type == "NThV_Conv" | clin_long$type == "NThV_Subtle"| clin_long$type == "NThV_SubtleMR", ]
NThVmod <-lmer( volume ~ type * amb + age+ sexbin + nonhiswhite + dur + types + standard+high +(1 | `Patient ID`) , data=NThV)
summary(NThVmod)
linearHypothesis(NThVmod, c("typeNThV_Subtle:amb"))
linearHypothesis(NThVmod, c("typeNThV_SubtleMR:amb"))
```


## NGMV

```{r}
NGMV <-clin_long[clin_long$type == "NGMV_Conv" | clin_long$type == "NGMV_Subtle"| clin_long$type == "NGMV_SubtleMR", ]
NGMVmod <-lmer( volume ~ type * amb + age+ sexbin + nonhiswhite + dur + types + standard+high +(1 | `Patient ID`) , data=NGMV)
summary(NGMVmod)
linearHypothesis(NGMVmod, c("typeNGMV_Subtle:amb"))
linearHypothesis(NGMVmod, c("typeNGMV_SubtleMR:amb"))
```

## NWMV

```{r}
NWMV <-clin_long[clin_long$type == "NWMV_Conv" | clin_long$type == "NWMV_Subtle"| clin_long$type == "NWMV_SubtleMR", ]
NWMVmod <-lmer( volume ~ type * amb + age+ sexbin + nonhiswhite + dur + types + standard+high +(1 | `Patient ID`) , data=NWMV)
summary(NWMVmod)
linearHypothesis(NWMVmod, c("typeNWMV_Subtle:amb"))
linearHypothesis(NWMVmod, c("typeNWMV_SubtleMR:amb"))
```

# Linear model with PDDS (continuous) as a predictor variable 

## T2LV

```{r}
T2LVmod2 <-lmer( volume ~ type * `PDDS Median` + age+ sexbin + nonhiswhite + dur + types + standard+high + (1 | `Patient ID`) , data=T2LV)
summary(T2LVmod2)
linearHypothesis(T2LVmod2, c("typeT2LV_Subtle:`PDDS Median`"))
linearHypothesis(T2LVmod2, c("typeT2LV_SubtleMR:`PDDS Median`"))
```

## T1Hypo

```{r}
T1Hypomod2 <-lmer( volume ~ type * `PDDS Median` + age+ sexbin + nonhiswhite + dur + types + standard+high + (1 | `Patient ID`) , data=T1Hypo)
summary(T1Hypomod2)
linearHypothesis(T1Hypomod2, c("typeT1Hypo_Subtle:`PDDS Median`"))
linearHypothesis(T1Hypomod2, c("typeT1Hypo_SubtleMR:`PDDS Median`"))
```


## TBV

```{r}
TBVmod2 <-lmer( volume ~ type * `PDDS Median` + age+ sexbin + nonhiswhite + dur + types + standard+high + (1 | `Patient ID`) , data=TBV)
summary(TBVmod2)
linearHypothesis(TBVmod2, c("typeTBV_Subtle:`PDDS Median`"))
linearHypothesis(TBVmod2, c("typeTBV_SubtleMR:`PDDS Median`"))
```

## CSF

```{r}
CSFmod2 <-lmer( volume ~ type * `PDDS Median` + age+ sexbin + nonhiswhite + dur + types + standard+high + (1 | `Patient ID`) , data=CSF)
summary(CSFmod2)
linearHypothesis(CSFmod2, c("typeCSF_Subtle:`PDDS Median`"))
linearHypothesis(CSFmod2, c("typeCSF_SubtleMR:`PDDS Median`"))
interact_plot(CSFmod2, pred = `PDDS Median`, modx = type)
```

## ICV

```{r}
ICVmod2 <-lmer( volume ~ type * `PDDS Median` + age+ sexbin + nonhiswhite + dur + types + standard+high + (1 | `Patient ID`) , data=ICV)
summary(ICVmod2)
linearHypothesis(ICVmod2, c("typeICV_Subtle:`PDDS Median`"))
linearHypothesis(ICVmod2, c("typeICV_SubtleMR:`PDDS Median`"))
```

## LThV

```{r}
LThVmod2 <-lmer( volume ~ type * `PDDS Median` + age+ sexbin + nonhiswhite + dur + types + standard+high + (1 | `Patient ID`) , data=LThV)
summary(LThVmod2)
linearHypothesis(LThVmod2, c("typeLThV_Subtle:`PDDS Median`"))
linearHypothesis(LThVmod2, c("typeLThV_SubtleMR:`PDDS Median`"))
```

## RThV

```{r}
RThVmod2 <-lmer( volume ~ type * `PDDS Median` + age+ sexbin + nonhiswhite + dur + types + standard+high + (1 | `Patient ID`) , data=RThV)
summary(RThVmod2)
linearHypothesis(RThVmod2, c("typeRThV_Subtle:`PDDS Median`"))
linearHypothesis(RThVmod2, c("typeRThV_SubteMR:`PDDS Median`"))
```

## GMV

```{r}
GMVmod2 <-lmer( volume ~ type * `PDDS Median` + age+ sexbin + nonhiswhite + dur + types + standard+high + (1 | `Patient ID`) , data=GMV)
summary(GMVmod2)
linearHypothesis(GMVmod2, c("typeGMV_Subtle:`PDDS Median`"))
linearHypothesis(GMVmod2, c("typeGMV_SubtleMR:`PDDS Median`"))
```

## WMV

```{r}
WMVmod2 <-lmer( volume ~ type * `PDDS Median` + age+ sexbin + nonhiswhite + dur + types + standard+high + (1 | `Patient ID`) , data=WMV)
summary(WMVmod2)
linearHypothesis(WMVmod2, c("typeWMV_Subtle:`PDDS Median`"))
linearHypothesis(WMVmod2, c("typeWMV_SubteMR:`PDDS Median`"))
```

## NBV

```{r}
NBVmod2 <-lmer( volume ~ type * `PDDS Median` + age+ sexbin + nonhiswhite + dur + types + standard+high + (1 | `Patient ID`) , data=NBV)
summary(NBVmod2)
linearHypothesis(NBVmod2, c("typeNBV_Subtle:`PDDS Median`"))
linearHypothesis(NBVmod2, c("typeNBV_SubtleMR:`PDDS Median`"))
interact_plot(NBVmod2, pred = `PDDS Median`, modx = type)
```


## NThV

```{r}
NThVmod2 <-lmer( volume ~ type * `PDDS Median` + age+ sexbin + nonhiswhite + dur + types + standard+high + (1 | `Patient ID`) , data=NThV)
summary(NThVmod2)
linearHypothesis(NThVmod2, c("typeNThV_Subtle:`PDDS Median`"))
linearHypothesis(NThVmod2, c("typeNThV_SubtleMR:`PDDS Median`"))
interact_plot(NThVmod2, pred = `PDDS Median`, modx = type)
```

## NGMV

```{r}
NGMVmod2 <-lmer( volume ~ type * `PDDS Median` + age+ sexbin + nonhiswhite + dur + types + standard+high + (1 | `Patient ID`) , data=NGMV)
summary(NGMVmod2)
linearHypothesis(NGMVmod2, c("typeNGMV_Subtle:`PDDS Median`"))
linearHypothesis(NGMVmod2, c("typeNGMV_SubtleMR:`PDDS Median`"))
interact_plot(NGMVmod2, pred = `PDDS Median`, modx = type)
```

## NWMV

```{r}
NWMVmod2 <-lmer( volume ~ type * `PDDS Median` + age+ sexbin + nonhiswhite + dur + types + standard+high + (1 | `Patient ID`) , data=NWMV)
summary(NWMVmod2)
linearHypothesis(NWMVmod2, c("typeNWMV_Subtle:`PDDS Median`"))
linearHypothesis(NWMVmod2, c("typeNWMV_SubtleMR:`PDDS Median`"))
interact_plot(NWMVmod2, pred = `PDDS Median`, modx = type)
```

# Linear model with MSRS-R as a predictor variable 

## T2LV

```{r,echo=FALSE}
T2LVmsrsmod <-lmer( volume ~ type * `MSRS-R Median` + age+ sexbin + nonhiswhite + dur + types+ standard+high + (1 | `Patient ID`) , data=T2LV)
summary(T2LVmsrsmod)
linearHypothesis(T2LVmsrsmod, c("typeT2LV_Subtle:`MSRS-R Median`"))
linearHypothesis(T2LVmsrsmod, c("typeT2LV_SubtleMR:`MSRS-R Median`"))
```

## T1Hypo

```{r,echo=FALSE}
T1Hypomsrsmod <-lmer( volume ~ type * `MSRS-R Median` + age+ sexbin + nonhiswhite + dur + types+ standard+high + (1 | `Patient ID`) , data=T1Hypo)
summary(T1Hypomsrsmod)
linearHypothesis(T1Hypomsrsmod, c("typeT1Hypo_Subtle:`MSRS-R Median`"))
linearHypothesis(T1Hypomsrsmod, c("typeT1Hypo_SubtleMR:`MSRS-R Median`"))
```

## TBV

```{r,echo=FALSE}
TBVmsrsmod <-lmer( volume ~ type * `MSRS-R Median` + age+ sexbin + nonhiswhite + dur + types+ standard+high + (1 | `Patient ID`) , data=TBV)
summary(TBVmsrsmod)
linearHypothesis(TBVmsrsmod, c("typeTBV_Subtle:`MSRS-R Median`"))
linearHypothesis(TBVmsrsmod, c("typeTBV_SubtleMR:`MSRS-R Median`"))
```

## CSF

```{r,echo=FALSE}
CSFmsrsmod <-lmer( volume ~ type * `MSRS-R Median` + age+ sexbin + nonhiswhite + dur + types+ standard+high + (1 | `Patient ID`) , data=CSF)
summary(CSFmsrsmod)
linearHypothesis(CSFmsrsmod, c("typeCSF_Subtle:`MSRS-R Median`"))
linearHypothesis(CSFmsrsmod, c("typeCSF_SubtleMR:`MSRS-R Median`"))
```

## ICV

```{r,echo=FALSE}
ICVmsrsmod <-lmer( volume ~ type * `MSRS-R Median` + age+ sexbin + nonhiswhite + dur + types+ standard+high + (1 | `Patient ID`) , data=ICV)
summary(ICVmsrsmod)
linearHypothesis(ICVmsrsmod, c("typeICV_Subtle:`MSRS-R Median`"))
linearHypothesis(ICVmsrsmod, c("typeICV_SubtleMR:`MSRS-R Median`"))
```

## LThV

```{r,echo=FALSE}
LThVmsrsmod <-lmer( volume ~ type * `MSRS-R Median` + age+ sexbin + nonhiswhite + dur + types+ standard+high + (1 | `Patient ID`) , data=LThV)
summary(LThVmsrsmod)
linearHypothesis(LThVmsrsmod, c("typeLThV_Subtle:`MSRS-R Median`"))
linearHypothesis(LThVmsrsmod, c("typeLThV_SubtleMR:`MSRS-R Median`"))
```

## RThV

```{r,echo=FALSE}
RThVmsrsmod <-lmer( volume ~ type * `MSRS-R Median` + age+ sexbin + nonhiswhite + dur + types+ standard+high + (1 | `Patient ID`) , data=RThV)
summary(RThVmsrsmod)
linearHypothesis(RThVmsrsmod, c("typeRThV_Subtle:`MSRS-R Median`"))
linearHypothesis(RThVmsrsmod, c("typeRThV_SubteMR:`MSRS-R Median`"))
interact_plot(RThVmsrsmod, pred = `MSRS-R Median`, modx = type)
```

## GMV

```{r,echo=FALSE}
GMVmsrsmod <-lmer( volume ~ type * `MSRS-R Median` + age+ sexbin + nonhiswhite + dur + types+ standard+high + (1 | `Patient ID`) , data=GMV)
summary(GMVmsrsmod)
linearHypothesis(GMVmsrsmod, c("typeGMV_Subtle:`MSRS-R Median`"))
linearHypothesis(GMVmsrsmod, c("typeGMV_SubtleMR:`MSRS-R Median`"))
```

## WMV

```{r,echo=FALSE}
WMVmsrsmod <-lmer( volume ~ type * `MSRS-R Median` + age+ sexbin + nonhiswhite + dur + types+ standard+high + (1 | `Patient ID`) , data=WMV)
summary(WMVmsrsmod)
linearHypothesis(WMVmsrsmod, c("typeWMV_Subtle:`MSRS-R Median`"))
linearHypothesis(WMVmsrsmod, c("typeWMV_SubteMR:`MSRS-R Median`"))
```


## NBV

```{r,echo=FALSE}
NBVmsrsmod <-lmer( volume ~ type * `MSRS-R Median` + age+ sexbin + nonhiswhite + dur + types+ standard+high + (1 | `Patient ID`) , data=NBV)
summary(NBVmsrsmod)
linearHypothesis(NBVmsrsmod, c("typeNBV_Subtle:`MSRS-R Median`"))
linearHypothesis(NBVmsrsmod, c("typeNBV_SubtleMR:`MSRS-R Median`"))
interact_plot(NBVmsrsmod,pred = `MSRS-R Median`, modx = type)
```

## NThV

```{r,echo=FALSE}
NThVmsrsmod <-lmer( volume ~ type * `MSRS-R Median` + age+ sexbin + nonhiswhite + dur + types+ standard+high + (1 | `Patient ID`) , data=NThV)
summary(NThVmsrsmod)
linearHypothesis(NThVmsrsmod, c("typeNThV_Subtle:`MSRS-R Median`"))
linearHypothesis(NThVmsrsmod, c("typeNThV_SubtleMR:`MSRS-R Median`"))
interact_plot(NThVmsrsmod,`MSRS-R Median`,type)
```


## NGMV

```{r,echo=FALSE}
NGMVmsrsmod <-lmer( volume ~ type * `MSRS-R Median` + age+ sexbin + nonhiswhite + dur + types+ standard+high + (1 | `Patient ID`) , data=NGMV)
summary(NGMVmsrsmod)
linearHypothesis(NGMVmsrsmod, c("typeNGMV_Subtle:`MSRS-R Median`"))
linearHypothesis(NGMVmsrsmod, c("typeNGMV_SubtleMR:`MSRS-R Median`"))
```


## NWMV

```{r,echo=FALSE}
NWMVmsrsmod <-lmer( volume ~ type * `MSRS-R Median` + age+ sexbin + nonhiswhite + dur + types+ standard+high + (1 | `Patient ID`) , data=NWMV)
summary(NWMVmsrsmod)
linearHypothesis(NWMVmsrsmod, c("typeNWMV_Subtle:`MSRS-R Median`"))
linearHypothesis(NWMVmsrsmod, c("typeNWMV_SubtleMR:`MSRS-R Median`"))
```


```{r}
NBVconv <- NBV[NBV$type=='NBV_Conv',]
NBVsub <- NBV[NBV$type=='NBV_Subtle',]
cor.test(NBVconv$volume,NBVconv$`PDDS Median`)
cor.test(NBVconv$volume,NBVconv$`MSRS-R Median`)
NThVconv <- NThV[NThV$type=='NThV_Conv',]
cor.test(NThVconv$volume,NThVconv$`PDDS Median`)
cor.test(NThVconv$volume,NThVconv$`MSRS-R Median`)
NGMVconv <- NGMV[NGMV$type=='NGMV_Conv',]
cor.test(NGMVconv$volume,NGMVconv$`PDDS Median`)
cor.test(NGMVconv$volume,NGMVconv$`MSRS-R Median`)
NWMVconv <- NWMV[NWMV$type=='NWMV_Conv',]
cor.test(NWMVconv$volume,NWMVconv$`PDDS Median`)
cor.test(NWMVconv$volume,NWMVconv$`MSRS-R Median`)
```

